---
title: "HomeWork 1"
author: "Wuraola Olawole"
date: "9/15/2020"
output: github_document
---

## Problem 1

### a. Create Data frame

```{r music_data_frame, message = FALSE}

library(tidyverse)

  music_df =
    
    tibble(
      
      music_num = rnorm(10),
              
      music_logical = music_num > 0,
              
      music_char = c("doh", "reh", "mi", "fah","soh", "lah", "ti", "d#", "r#", "f#" ),
              
      music_factor = factor(c("low", "low", "low", "mod", "mod", "mod", "high", "high", "high", "high"))
)

```
### b. Mean of each variable in music_df

```{r mean_music_pull_var, message = FALSE, warning = FALSE}

  mean(pull(music_df, music_num))

  mean(pull(music_df, music_logical))
  
  mean(pull(music_df, music_char))
  
  mean(pull(music_df, music_factor))

```
I can't take the mean of the Character and factor variables

Only the means of numerical and logical variables can be taken

### c. Use as.numeric function

```{r music_convert_num, message = FALSE, results = 'hide', warning = FALSE}
  
  as.numeric(pull(music_df, music_logical))
  
  as.numeric(pull(music_df, music_char))
  
  as.numeric(pull(music_df, music_factor))
  
```
I am able to convert the logical and factor variables to numeric values

However, I Was unable to convert the character variables to numeric values
directly

### d. Convert music_logical to Num and factor 
```{r music_convert_factor, warning = FALSE}
  
  as.numeric(pull(music_df, music_logical)) * pull(music_df, music_num)
  
  as.factor(pull(music_df, music_logical)) * pull(music_df, music_num)
  
  as.numeric(as.factor(pull(music_df, music_logical))) * pull(music_df, music_num)
```


## Problem 2

### a. Install palmerpenguins and describe data set

```{r penguins_dataset}
  
  data("penguins", package = "palmerpenguins")
  
```

```{r summary_penguin_var, include = FALSE}
  sum_species = summary(pull(penguins, species))

  sum_body_mass = summary(pull(penguins, body_mass_g )) 
  
  sum_bill_len = summary(pull(penguins, bill_length_mm ))
  
  sum_bill_dep = summary(pull(penguins, bill_depth_mm ))
  
  sum_flip = summary(pull(penguins, flipper_length_mm ))
  
```


This data set contains the `r names(penguins)` (of data collection) of `r nrow (penguins)` penguins.

The 3 species used in this data set were: `r names (sum_species)` and they were `r 

sum_species` respectively. The average body mass in grams of these penguins was `r 

round (sum_body_mass [4], digits = 2)`, the average bill length in mm of these penguins was `r 

round (sum_bill_len [4], digits = 2)`, the average bill depth in mm of these penguins was `r 

round (sum_bill_dep [4], digits = 2)`, and the average flipper length in mm of these penguins was `r 

round (sum_flip [4], digits = 2 )`.  In this data set there were `r nrow (penguins)` rows and `r 

ncol (penguins)` columns. 


### b. Plot flipper length against bill length

```{r Penguin_plot, warning = FALSE}

  ggplot(
    
    penguins, 
    
    aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + 
    
  geom_point(shape = 16) + ggtitle("Comparison of Flipper and bill lengths in 3 species of Penguins")

  ggsave("penguins.pdf")

```


